---
title: "Gun Control Chi-Square"
author: "Kelly Odion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Kelly and I'm updating this markdown file

Load packages and data:

```{r}
library(tidyverse)

gc <- read_csv("gc_df.csv")
```

Is there a signficant difference in recommended gun control action in male and female respondents (should guns be easier, harder, or the same difficulty to get)? 



Hey (Chase)

Kelly: data wrangling and counts 

```{r}
get_guns <- gc %>% 
  filter(gender!= "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
```

My name is Chase the collaborator and I'm going to be doing chi-square test for independence!

We ask "Is there a signficant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}
# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop


# Run chi-square test for independence

guns_x2 <- chisq.test(get_guns)
guns_x2
```

"Recommended government action on gun access differed significantly between male (n = ) and female (n = ) respondants ($\chi^2$(`r guns_x2$parameter`" = ......, p < 0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compared to 40.4% for male respondants.